\documentclass[
	a4paper,
	12pt,
]{resume}

\usepackage[scaled]{helvet} % Helvetica-like

\usepackage[none]{hyphenat} % disable hyphens
\sloppy

\renewcommand{\familydefault}{\sfdefault}

\name{William Jeynes} 

\begin{document}

\begin{center}
\href{mailto:will@jeynes.uk}{will@jeynes.uk} \vertline \href{tel:07413494620}{07413 494620}

\ulhref{https://www.linkedin.com/in/william-jeynes/}{linkedin.com/in/william-jeynes/} \vertline \ulhref{https://jeynes.uk/}{jeynes.uk}

\end{center}

\begin{rSection}{Experience}

\begin{rWorksection}{DFDS}{2024-2025}{Student Software Engineer}
\item Collaborated with a large multidisciplinary team across the continent to deliver a high standard of always-on applications, processing millions of tonnes of cargo a week across six freight terminals.
\item Migrated legacy solutions and processes from VB6 and MSSQL into future proof, cloud-based C\# .NET applications across all areas of terminal operations, increasing uptime and efficiency. 
\item Worked in a team to re-make automotive operations at DFDS in a matter of months, our system now processes around 10,000 cars a week.
\item Spearheaded the team's first React JS web-app, helped drive office code standards to include unit and integration testing, migrated processes to Kubernetes and drove cloud-based componentisation.
\item Setup a Kafka-connect cluster to allow seamless integration with legacy backends and modern cloud components which processes over a million messages a day.
\item Maintained a high level of commitment and responsibility in an emerging technical field. Provided out of hours support, managed go-lives and dealt directly with stakeholders from all levels to force through positive change in a legacy sector and otherwise overlooked industry. (\ulhref{https://jeynes.uk/posts/2025-03-03-DFDS-Kafka}{More information on my website}) 
\end{rWorksection}
	
\begin{rWorksection}{Everbit (Mobile Consultancy Startup)}{2023-2024}{Software Engineer}
\item As part of a small team, developed mobile applications for a range of clients with strict time-based and monetary constraints, for example Meals (\ulhref{https://apps.apple.com/gb/app/meals-healthy-recipes-diet/id1456722282}{live on the apple appstore}) and Wellmatch.
\item Implemented features across the tech stack: frontends in Flutter, with Firebase and PHP backends. (\ulhref{https://jeynes.uk/posts/2024-01-01-Meals}{More information on my website}) 
\end{rWorksection}

\begin{rWorksection}{DFDS}{2023}{Student Backend Developer}
\item Developed critical applications for gate security operations, consolidating control from a range of applications to one platform, saving time and reducing human errors. 
\item Worked collaborativley to create a fullstack project developing a Flutter application with a C\# backend to sit as a temporary bridge between a monolith stack and new modern gate components.
\end{rWorksection}
	
\begin{rWorksection}{Lyke (Web-Dev Company)}{2023}{Software Developer}
\item Implemented PHP projects such as an in-house CRM and an OpenIDConnect server for cross-platform single sign on.
\end{rWorksection}


\end{rSection}

\newpage


\begin{rSection}{Education}

\begin{rEdusection}{University of Sheffield: Computer Science with a Year in Industry (BSc)}{2022-2026}
\item Module average to date is 80\%. Examples of third year modules include Advanced Algorithms, Software Reingineering and Mobile Development.
\item Completed a large number of group programming and research assignments to a very high standard.
\item Co-founded Sheffield Game Development Society in first year, which is now in third year of operation. I am currently the Secretary and Deputy President, for which I have run tutorials, workshops and provided technical assistance such as website setup.
\item Dissertation thesis on using large language models for disinformation analysis, using cutting edge techniques to push commercial language models to their limit, in combination with research-backed techniques to to verify authenticity.
\end{rEdusection}
	
\begin{rEdusection}{Franklin Sixth Form College}{2020-2022}
\item \textbf{A*} A-Level Computer Science 
\item \textbf{A*} A-Level Further Maths
\item \textbf{A*} A-Level Maths
\item \textbf{A} A-Level Physics
\item \textbf{B} Extended Project Qualification
\end{rEdusection}

\begin{rEdusection}{Healing School, A Science Academy}{2015-2020}
\item 10 GCSEs: \textbf{9, 9, 9, 9, 9, 8, 8, 8, 7, 7}
\item BTEC Creative IMedia: \textbf{Distinction}
\end{rEdusection}
	
\end{rSection}



\begin{rSection}{Skills \& Abilities}

\begin{rListsection}
\item Experience developing software in a range of technologies and environments. Key technologies: AWS, Terragrunt (Terraform/OpenTofu), C\#, Flutter, PHP, Java, ReactJS, Kafka, Kubernetes (Docker + Linux), Entity Framework (MSSQL), Oauth (Active Directory), Windows Server, Azure Devops Pipelines.
\item Implemented both legacy monolith solutions in languages like Visual Basic up to modern cloud native applications in AWS. Have done extensive work combining the two using technologies like Kafka. 
\item Extensive experience at stakeholder management evidenced by presentations in sprint reviews, to both technical and non-technical parties.
\item Experienced at solving complex production issues in out of hours support.
\item Been part of go-live teams across Europe, providing extensive training and help to end-users.
\item Experience working in multi-disciplinary teams across time zones, efficient in both scrum and kanban setups.
\item Teaching and presentation experience, from knowledge-sharing with colleages in areas of personal expertise, to delivering taught tutorial sessions for Game Development Society.
\item Experience in using Linux and the Open Source ecosystem, professionally and personally, with Linux being my daily-driver.
\item Quick to lean new languages and technologies. I often do personal projects to elevate my understanding of interesting subject areas, and I try to solve my own problems with code.
\end{rListsection}

\end{rSection}

\end{document}

% Original Template:
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Medium Length Professional CV
% LaTeX Template
% Version 3.0 (December 17, 2022)
%
% This template originates from:
% https://www.LaTeXTemplates.com
%
% Author:
% Vel (vel@latextemplates.com)
%
% Original author:
% Trey Hunner (http://www.treyhunner.com/)
%
% License:
% CC BY-NC-SA 4.0 (https://creativecommons.org/licenses/by-nc-sa/4.0/)
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
